A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-06 paper.tex
Adding results CSVs and structure

@@

@@

@@

@@

\begin{equation}
  A_{iCoA} = \dfrac{\sum_{i=1}^{N} i\mu_{A}(x) x_{i}}{\sum_{i=1}^{N}
    i\mu_{A}(x)}
\end{equation}

@@

% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=2.5in]{myfigure}
%   where an .eps filename suffix will be assumed under latex, 
%   and a .pdf suffix will be assumed for pdflatex; or what has been declared
%   via \DeclareGraphicsExtensions.
%   \caption{Simulation results for the network.}
%   \label{fig_sim}
% \end{figure}

@@

@@

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
% 
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
% 
% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=2.5in]{myfigure}
%   where an .eps filename suffix will be assumed under latex, 
%   and a .pdf suffix will be assumed for pdflatex; or what has been declared
%   via \DeclareGraphicsExtensions.
%   \caption{Simulation results for the network.}
%   \label{fig_sim}
% \end{figure}

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
% 
% \begin{table}[!t]
%%   increase table row spacing, adjust to taste
%   \renewcommand{\arraystretch}{1.3}
%   if using array.sty, it might be a good idea to tweak the value of
%   \extrarowheight as needed to properly center the text within the cells
%   \caption{An Example of a Table}
%   \label{table_example}
%   \centering

@@

@@

\section{Throwing References}

\cite{atanassov1986intuitionistic}
\cite{atanassov2003intuitionistic}
\cite{davarzani2013novel}
\cite{despi2013generalised}
\cite{sharma2011cut}
\cite{sharma2011cutgroups}
\cite{akram2014intuitionistic}
\cite{cornelis2001compositional}
\cite{castillo2007intuitionistic}
\cite{bustince1995method}
\cite{marinov2005method}
\cite{atanassov2013intuitionistic}
\cite{zadeh1965fuzzy}
\cite{klir1995fuzzy}
\cite{pedrycz1998shadowed}
\cite{mendel2001uncertain}
\cite{mendel2002type}
\cite{liang2000interval}
\cite{mendel2006interval}
\cite{karnik2001centroid}
\cite{castro2007interval}
\cite{wagner2013juzzy}

>>>>

What is a fuzzy set? \cite{zadeh1965fuzzy}

What is fuzzy logic? \cite{klir1995fuzzy}

Types of fuzzy sets. Mendel book \cite{mendel2001uncertain}

What is a fuzzy inference system?

There can be different types. Type-2 \cite{mendel2002type}, interval
t2 \cite{liang2000interval} and \cite{mendel2006interval}

Type-2 is time-consuming. Shadowed sets \cite{pedrycz1998shadowed}

What is a intuitionistic fuzzy set? \cite{atanassov1986intuitionistic}
\cite{atanassov2003intuitionistic} \cite {despi2013generalised}

@@

Application of intuitionistic fuzzy sets, bacillus colonies
recognition \cite{davarzani2013novel}

Alpha cut \cite{sharma2011cut} \cite{sharma2011cutgroups}

intuitionistic inference engine \cite{cornelis2001compositional}

implementation of a ifis, castillo \cite{castillo2007intuitionistic}

more inference \cite{bustince1995method}

centroid of a type-2 fuzzy-set \cite{karnik2001centroid}

and even more inference \cite{marinov2005method}

Intuitionistic control washing machines \cite{akram2014intuitionistic}

@@

Define in more detail intuitionistic fuzzy sets.

Formulas and basic explanation (below) \cite{atanassov2013intuitionistic}

@@

How a classic fuzzy set is represented as a ifs. How an intuitionistic
fuzzy set is represented in this work.

How the non-membership is going to affect the membership (show
formula). Present both examples (stating the parameters).

How the coa is calculated (show formula and plot). How the formula can
be contracted.

@@

%iCoA contracted
\begin{equation}
  A_{iCoA} = \dfrac{\sum_{i=1}^{N} i\mu_{A}(x) x_{i}}{\sum_{i=1}^{N}
    i\mu_{A}(x)}
\end{equation}

@@

Comparisons against juzzy \cite{wagner2013juzzy}

Compare using Mackey-Glass, 100 training, 50 for testing, because it
took too much time. Genetic algorithm. Present parameters: mean 0-100,
sd 30-70, mf 1, nmf 0.8-1.0.

The rule base.

@@

Results can be found on https://github.com/amherag/wcci-2016-a

@@

@@

This work mainly focuses on proving that the design is viable, but it
also proves that at least in some cases the intuitionistic fis can
out-perform the t1 and t2.

@@

We want to create a toolbox such as \cite{castro2007interval}
We want to experiment with other data sets.
We want to speed up the algorithm.
We want to experiment with generalized type-2.
